Synthesizing Symmetric Lenses

### 2018-07-11 papers/SymmetricLenses/main.tex
edits to section 1 and section 2

@@

%Consider the trivial lens
%\lstinline{disc(emp_salary,emp_row,rep(emp_salary),rep(emp_row))}. As this is
%the disconnect lens, the cost of each side is the entropy of the data format, so
%the total cost is $\EntropyOf{\lstinline{emp_salary}} +
%\EntropyOf{\lstinline{emp_row}}$. \lstinline{emp_salary} contains strictly more
%imformation than \EntropyOf{\lstinline{": " . salary}}, and \lstinline{emp_row}
%contains strictly more information than \EntropyOf{\lstinline{": " . salary}},
%so by our metric \lstinline{single_emp_map} is preferable to the disconnect
%lens.
Consider the trivial lens
\lstinline{disc(emp_salary,emp_row,rep(emp_salary),rep(emp_row))}. As this is
the disconnect lens, the cost of each side is the entropy of the data format, so
the total cost is $\EntropyOf{\lstinline{emp_salary} } +
\EntropyOf{\lstinline{emp_row}}$. \lstinline{emp_salary} contains strictly more
information than $\EntropyOf{\lstinline{": " . salary}}$, and
\lstinline{emp_row} contains strictly more information than
\EntropyOf{\lstinline{": " . salary}}, so by our metric
\lstinline{single_emp_map} is preferable to the disconnect lens.
% end overview

>>>>

%%As a further example, consider the trivial lens
%%\lstinline{disc(emp_salary,emp_row,rep(emp_salary),rep(emp_row))}. As this is
%%the disconnect lens, the cost of each side is the entropy of the data format, so
%%the total cost is $\EntropyOf{\lstinline{emp_salary} } +
%%\EntropyOf{\lstinline{emp_row}}$. The lens \lstinline{emp_salary} contains strictly more
%%information than $\EntropyOf{\lstinline{": " . salary}}$, and
%%\lstinline{emp_row} contains strictly more information than
%%\EntropyOf{\lstinline{": " . salary}}, so by our metric
%%\lstinline{single_emp_map} is preferable to the disconnect lens.

@@

%Consider the trivial lens
%\lstinline{disc(emp_salary,emp_row,rep(emp_salary),rep(emp_row))}. As this is
%the disconnect lens, the cost of each side is the entropy of the data format, so
%the total cost is $\EntropyOf{\lstinline{emp_salary}} +
%\EntropyOf{\lstinline{emp_row}}$. \lstinline{emp_salary} contains strictly more
%imformation than \EntropyOf{\lstinline{": " . salary}}, and \lstinline{emp_row}
%contains strictly more information than \EntropyOf{\lstinline{": " . salary}},
%so by our metric \lstinline{single_emp_map} is preferable to the disconnect
%lens.
% end overview
